---
title: "A study of changes in short chain fatty acids (SCFA) in women during pregnancy whose children developed asthma"
subtitle: "Without covariate adjustment"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  html_document: 
    toc: true
    theme: united
---

```{r setup, warning=FALSE, message=FALSE}
# rm(list = ls())
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, 
                      message = FALSE, comment = NA,
                      fig.width = 6.25, fig.height = 5)
options(qwraps2_markup = "markdown",
        qwraps2_frmt_digits = 2)

library(openxlsx)
library(tidyverse) 
library(vegan)
library(CLME)
library(magrittr)
library(qwraps2)
library(ggprism)
library(ggsci)
library(ggpubr)
library(rstatix)
library(jtools)
```

```{r helper}
plot_box = function(data, group_lab, group_var, key_var, adjust_var, title, y.position, step.increase) {
  
  select_vars = function() {
    any_of(c(group_var, key_var, adjust_var))
  }
  df_fig = data %>%
    dplyr::select(select_vars()) %>%
    mutate(group = get(group_var), value = get(key_var))
  
  bxp = ggboxplot(df_fig, x = "group", y = "value", color = "group",
                  add = "jitter", xlab = FALSE, ylab = FALSE, title = title) +
    scale_color_npg(name = str_to_title(group_var)) +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          strip.background = element_rect(fill = "white"),
          legend.position = "bottom",
          plot.title = element_text(hjust = 0.5))
  
  if (!is.null(adjust_var)) {
    lm_formula = paste("value ~ group + ", paste(adjust_var, collapse = " + "))
    lm_fit = lm(as.formula(lm_formula), data = df_fig)
    df_p = data.frame(group1 = "No", group2 = "Yes",
                      p = summary(lm_fit)$coef[grepl("group", names(coef(lm_fit))), "Pr(>|t|)"]) %>%
      mutate(p = round(p, 2))
    
    bxp = bxp + 
      stat_pvalue_manual(df_p, y.position = y.position, 
                         step.increase = step.increase, label = "p")
  } else {
    bxp = bxp + 
      stat_compare_means(method = "wilcox.test", label.x = 1.5, label = "p.format")
  }
  return(bxp)
}

plot_clme = function(clme_obj, group, y_min, y_max, p_gap, fill_lab = "Wheezing", ...) {
  p_val = clme_obj$p.value
  est_mean = clme_obj$theta[group]
  est_se = sqrt(diag(clme_obj$cov.theta))[group]
  
  df_fig = data.frame(x = group, y = est_mean, err = est_se)
  
  if (max(est_mean) >= min(est_mean)) {
    df_p = data.frame(group1 = group[seq_len(length(group) - 1)],
                      group2 = group[-1],
                      x = group[-1],
                      label = paste0("p = ", round(p_val, 3)),
                      y.position = seq.int(from = est_mean[2] + p_gap, 
                                           to = ifelse(est_mean[2] < max(est_mean), 
                                                       max(est_mean) + p_gap, 
                                                       max(est_mean) + 2 * p_gap), 
                                           length.out = length(group) - 1))
  } else {
    df_p = data.frame(group1 = group[seq_len(length(group) - 1)],
                      group2 = group[-1],
                      x = group[-1],
                      label = paste0("p = ", round(p_val, 3)),
                      y.position = seq.int(from = ifelse(est_mean[1] > min(est_mean), 
                                                         est_mean[1] + p_gap, 
                                                         est_mean[1] + 2 * p_gap),
                                           to = min(est_mean) + p_gap, 
                                           length.out = length(group) - 1))
  }
  
  
  fig = df_fig %>%
    ggplot(aes(x = x, y = y)) +
    geom_bar(stat = "identity", color = "black", aes(fill = x)) + 
    geom_errorbar(aes(ymin = y - 1.96 * err, ymax = y + 1.96 * err), 
                  width = .2, position = position_dodge(.9)) +
    add_pvalue(df_p,
               xmin = "group1",
               xmax = "group2",
               label = "label",
               y.position = "y.position",
               remove.bracket = FALSE, 
               ...) +
    ylim(y_min, y_max) +
    theme_bw() +
    scale_fill_npg(name = fill_lab) +
    theme(panel.border = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          axis.line = element_line(size = 0.5),
          plot.title = element_text(hjust = 0.5))
  return(fig)
}

fisher_z = function(data, var1, var2, group) {
   select_vars = function() {
    any_of(c(var1, var2, group))
  }
  df = data %>%
    dplyr::select(select_vars()) %>%
    mutate(var1 = get(var1), 
           var2 = get(var2),
           group = get(group))
  group_level = sort(unique(df$group))
  
  # Create two vectors of data
  x1 = df %>%
    filter(group == group_level[1]) %>%
    dplyr::select(var1) %>%
    .$var1
  y1 = df %>%
    filter(group == group_level[1]) %>%
    dplyr::select(var2) %>%
    .$var2
  x2 = df %>%
    filter(group == group_level[2]) %>%
    dplyr::select(var1) %>%
    .$var1
  y2 = df %>%
    filter(group == group_level[2]) %>%
    dplyr::select(var2) %>%
    .$var2
  
  # Calculate Pearson correlation coefficients
  r1 = cor(x1, y1)
  r2 = cor(x2, y2)
  
  # Convert correlation coefficients to z-scores using Fisher's z-transformation
  z1 = atanh(r1)
  z2 = atanh(r2)
  
  # Calculate the difference between the two z-scores
  z_diff = z1 - z2
  
  # Calculate the standard error of the difference between the two z-scores
  se_z_diff = sqrt((1/(length(x1) - 3)) + (1/(length(x2) - 3)))
  
  # Calculate the test statistic
  test_statistic = z_diff / se_z_diff
  
  # Calculate the p-value
  p_value = 2 * min(pnorm(abs(test_statistic)), 
                    pnorm(abs(test_statistic), lower.tail = FALSE))
  return(p_value)
}
```

# 1. Import data 

```{r}
df_meta = read.xlsx("../data/eager_scfa_samples_matched.xlsx")
df_meta$visit = recode(df_meta$visit, R = "20wks", S = "28wks")
df_meta$wheezing = recode(df_meta$wheezing, `0` = "No", `1` = "Yes")
df_meta$wheezing = factor(df_meta$wheezing)
df_meta$education = factor(df_meta$education,
                           levels = c("Not High-school graduate",
                                      "High-school graduate",
                                      "> High School"))
df_meta$income = factor(df_meta$income)
df_meta$sex_fetus1 = factor(df_meta$sex_fetus1)

df_scfa_raw = read.xlsx("../data/Short-Chain Fatty Acid Analysis Result_Creative Proteomics_CPLC05192202-2.xlsx")

df_loq = df_scfa_raw[3:9, 13:14]
colnames(df_loq) = c("SCFA", "LOQ")

df_scfa_na = df_scfa_raw[-1, 1:12]
colnames(df_scfa_na) = c("Sample", "Barcode1", "Barcode2", "Box_Id", "Sample_Type",
                         "Acetic", "Propionic", "Isobutyric", "Butyric",
                         "Isovaleric", "Valeric", "Hexanoic")
df_scfa_na = df_scfa_na %>%
  mutate_at(vars(Acetic:Hexanoic), as.numeric)
df_merge_na = df_meta %>%
  dplyr::left_join(df_scfa_na, by = c("Barcode1", "Barcode2", "Box_Id"))

df_scfa = df_scfa_na %>%
  replace_na(list(Acetic = df_loq$LOQ[1]/2,
                  Propionic = df_loq$LOQ[2]/2,
                  Isobutyric = df_loq$LOQ[3]/2,
                  Butyric = df_loq$LOQ[4]/2,
                  Isovaleric = df_loq$LOQ[5]/2,
                  Valeric = df_loq$LOQ[6]/2)) %>%
  dplyr::mutate(total = rowSums(across(Acetic:Valeric)))
df_merge = df_meta %>%
  dplyr::left_join(df_scfa, by = c("Barcode1", "Barcode2", "Box_Id"))
df_v1 = df_merge %>%
  filter(visit == "20wks")
df_v2 = df_merge %>%
  filter(visit == "28wks")
```

# 2. Descriptive statistics {.tabset}

## Total SCFA concentrations by groups

### At 20 weeks

```{r}
p_total = ggviolin(df_v1, x = "wheezing", y = "total", color = "wheezing",
                   add = "boxplot", xlab = "Wheezing", ylab = "Total SCFAs") +
  stat_compare_means(method = "wilcox.test", label.x = 1.5, label = "p.format") +
  scale_color_npg(name = NULL)
p_total
ggsave("../results/figures/supp_violine_total_v1.jpeg", width = 6.25, height = 5, dpi = 100)
ggsave("../results/figures/supp_violine_total_v1.pdf", width = 6.25, height = 5)
```

### At 28 weeks

```{r}
p_total = ggviolin(df_v2, x = "wheezing", y = "total", color = "wheezing",
                   add = "boxplot", xlab = "Wheezing", ylab = "Total SCFAs") +
  stat_compare_means(method = "wilcox.test", label.x = 1.5, label = "p.format") +
  scale_color_npg(name = NULL)
p_total
ggsave("../results/figures/supp_violine_total_v2.jpeg", width = 6.25, height = 5, dpi = 100)
ggsave("../results/figures/supp_violine_total_v2.pdf", width = 6.25, height = 5)
```

## SCFA change over time (28 weeks - 20 weeks)

```{r, fig.width=10, fig.height=6}
df_pair = df_v1 %>%
  dplyr::select(Study_ID, Acetic:Valeric) %>%
  dplyr::inner_join(
    df_v2 %>%
      dplyr::select(Study_ID, Acetic:Valeric),
    suffix = c("_v1", "_v2"),
    by = "Study_ID"
  ) %>%
  dplyr::mutate(across(ends_with("_v2"),
                       ~ . - get(str_replace(cur_column(), "_v2$", "_v1")),
                       .names = "diff_{str_replace(.col, '_v2$', '')}")) %>%
  dplyr::left_join(df_v1 %>%
                     dplyr::select(Study_ID, wheezing),
                   by = "Study_ID")

var_list = c("Acetic", "Propionic", "Isobutyric", 
             "Butyric", "Isovaleric", "Valeric")
title_list = c("Acetic Acid", "Propionic Acid", "Isobutyric Acid", 
               "Butyric Acid", "Isovaleric Acid", "Valeric Acid")
y_pos_list = c(6, 0.5, 0.1, 0.25, 0.09, 0.015)
step_list = c(0.1, 0.1, 0.1, 0.1, 0.01, 0.005)

bxp_list = list()
for (i in seq_along(var_list)) {
  var = paste0("diff_", var_list[[i]])
  title = title_list[[i]]
  df = df_pair %>%
    dplyr::transmute(value = get(var), group = wheezing)
  bxp = df %>%
    ggboxplot(x = "group", y = "value", color = "group",
              add = "jitter", xlab = FALSE, ylab = FALSE, title = title) +
    stat_compare_means(method = "wilcox.test", label.x = 1.5, label = "p.format") +
    scale_color_npg(name = "Wheezing") +
    theme(axis.text.x = element_blank(),
          axis.ticks.x = element_blank(),
          strip.background = element_rect(fill = "white"),
          legend.position = "bottom",
          plot.title = element_text(hjust = 0.5))
    
  bxp_list[[i]] = bxp
}

p_box = ggarrange(bxp_list[[1]], bxp_list[[2]], bxp_list[[3]], 
                  bxp_list[[4]], bxp_list[[5]], bxp_list[[6]], 
                  ncol = 3, nrow = 2, 
                  common.legend = TRUE, legend = "bottom")
p_box
ggsave("../results/figures/supp_box_plot_time_change.jpeg", width = 10, height = 6, dpi = 100)
ggsave("../results/figures/supp_box_plot_time_change.pdf", width = 10, height = 6)
```

## Alpha diversities

```{r}
shannon_index = diversity(df_merge %>%
                            dplyr::select(Acetic:Valeric))
df_shannon = df_merge %>%
  dplyr::select(Study_ID, wheezing, visit) %>%
  dplyr::mutate(shannon_index = shannon_index)

p_box_alpha = df_shannon %>% 
  ggboxplot(x = "wheezing", y = "shannon_index", color = "wheezing", 
            facet.by = "visit", xlab = "Wheezing", ylab = "Shannon Index",
            add = "jitter") +
  stat_compare_means(method = "wilcox.test", label.x = 1.5, label = "p.format") +
  scale_color_npg(name = NULL)

p_box_alpha
ggsave("../results/figures/supp_box_plot_alpha.jpeg", width = 6.25, height = 5, dpi = 100)
ggsave("../results/figures/supp_box_plot_alpha.pdf", width = 6.25, height = 5)
```

# 3. Two-group comparisons

1. SCFAs by the outcome variable (any report of asthma or wheezing since birth).

2. P-values were determined by two-sided Wilcoxon rank sum test.

3. Subfigure a: at 20 weeks, subfigure b: at 28 weeks.

```{r, fig.width=14, fig.height=10}
var_list = c("Acetic", "Propionic", "Isobutyric", 
             "Butyric", "Isovaleric", "Valeric")
title_list = c("Acetic Acid", "Propionic Acid", "Isobutyric Acid", 
               "Butyric Acid", "Isovaleric Acid", "Valeric Acid")
y_pos_list = c(6, 0.5, 0.1, 0.25, 0.09, 0.015)
step_list = c(0.1, 0.1, 0.1, 0.1, 0.01, 0.005)

bxp_list_v1 = list()
for (i in seq_along(var_list)) {
  bxp = plot_box(data = df_v1,
                 group_var = "wheezing",
                 key_var = var_list[i], 
                 adjust_var = NULL,
                 title = title_list[i],
                 y.position = y_pos_list[i], 
                 step.increase = step_list[i])
  bxp_list_v1[[i]] = bxp
}

bxp_list_v2 = list()
for (i in seq_along(var_list)) {
  bxp = plot_box(data = df_v2,
                 group_var = "wheezing",
                 key_var = var_list[i], 
                 adjust_var = NULL,
                 title = title_list[i],
                 y.position = y_pos_list[i], 
                 step.increase = step_list[i])
  bxp_list_v2[[i]] = bxp
}

p_box = ggarrange(bxp_list_v1[[1]], bxp_list_v1[[2]], bxp_list_v1[[3]], 
                  bxp_list_v1[[4]], bxp_list_v1[[5]], bxp_list_v1[[6]], 
                  bxp_list_v2[[1]], bxp_list_v2[[2]], bxp_list_v2[[3]], 
                  bxp_list_v2[[4]], bxp_list_v2[[5]], bxp_list_v2[[6]], 
                  ncol = 6, nrow = 2, 
                  labels = c("a", "", "", "", "", "",
                             "b", "", "", "", "", ""), 
                  common.legend = TRUE, legend = "bottom")
p_box
ggsave("../results/figures/supp_box_plot.jpeg", width = 12, height = 10, dpi = 100)
ggsave("../results/figures/supp_box_plot.pdf", width = 12, height = 10)
```

# 4. Trend test

1. SCFAs by the outcome variable (any report of asthma or wheezing since birth).

2. P_values were determined by CLME.

```{r}
df_merge$wheezing = factor(df_merge$wheezing, ordered = TRUE,
                           levels = c("No", "Yes"))
```

## 4.1 At 20 weeks {.tabset}

### Monotonic increasing trend

```{r, fig.width=12, cache=TRUE}
cons = list(order = "simple", decreasing = FALSE, node = 1)

fit1 = clme(Acetic ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit2 = clme(Propionic ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit3 = clme(Isobutyric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit4 = clme(Butyric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit5 = clme(Isovaleric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit6 = clme(Valeric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)

summ_fit1 = summary(fit1)
summ_fit2 = summary(fit2)
summ_fit3 = summary(fit3)
summ_fit4 = summary(fit4)
summ_fit5 = summary(fit5)
summ_fit6 = summary(fit6)

fig1 = plot_clme(summ_fit1, group = c("No", "Yes"), 
                 y_min = 0, y_max = 4.5, p_gap = 1.2) +
  labs(x = NULL, y = "Concentration", title = "Acetic Acid")
fig2 = plot_clme(summ_fit2, group = c("No", "Yes"), 
                 y_min = -0.2, y_max = 0.5, p_gap = 0.3) +
  labs(x = NULL, y = "Concentration", title = "Propionic Acid")
fig3 = plot_clme(summ_fit3, group = c("No", "Yes"), 
                 y_min = -0.2, y_max = 0.4, p_gap = 0.25) +
  labs(x = NULL, y = "Concentration", title = "Isobutyric Acid")
fig4 = plot_clme(summ_fit4, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.35, p_gap = 0.15) +
  labs(x = NULL, y = "Concentration", title = "Butyric Acid")
fig5 = plot_clme(summ_fit5, group = c("No", "Yes"),
                 y_min = 0, y_max = 0.12, p_gap = 0.05) +
  labs(x = NULL, y = "Concentration", title = "Isovaleric Acid")
fig6 = plot_clme(summ_fit6, group = c("No", "Yes"), 
                 y_min = -0.01, y_max = 0.02, p_gap = 0.01) +
  labs(x = NULL, y = "Concentration", title = "Valeric Acid")

p_clme1 = ggarrange(fig1, fig2, fig3, fig4, fig5, fig6, 
                    ncol = 6, common.legend = TRUE, legend = "bottom")
p_clme1
ggsave("../results/figures/supp_clme_plot_v1_increase.jpeg", width = 12, height = 5, dpi = 100)
ggsave("../results/figures/supp_clme_plot_v1_increase.pdf", width = 12, height = 5)
```

### Monotonic decreasing trend

```{r, fig.width=12, cache=TRUE}
cons = list(order = "simple", decreasing = TRUE, node = 1)

fit1 = clme(Acetic ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit2 = clme(Propionic ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit3 = clme(Isobutyric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit4 = clme(Butyric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit5 = clme(Isovaleric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)
fit6 = clme(Valeric ~ wheezing, 
            data = df_v1, constraints = cons, seed = 123)

summ_fit1 = summary(fit1)
summ_fit2 = summary(fit2)
summ_fit3 = summary(fit3)
summ_fit4 = summary(fit4)
summ_fit5 = summary(fit5)
summ_fit6 = summary(fit6)

fig1 = plot_clme(summ_fit1, group = c("No", "Yes"), 
                 y_min = 0, y_max = 4.5, p_gap = 1.2) +
  labs(x = NULL, y = "Concentration", title = "Acetic Acid")
fig2 = plot_clme(summ_fit2, group = c("No", "Yes"), 
                 y_min = -0.2, y_max = 0.5, p_gap = 0.3) +
  labs(x = NULL, y = "Concentration", title = "Propionic Acid")
fig3 = plot_clme(summ_fit3, group = c("No", "Yes"), 
                 y_min = -0.2, y_max = 0.4, p_gap = 0.3) +
  labs(x = NULL, y = "Concentration", title = "Isobutyric Acid")
fig4 = plot_clme(summ_fit4, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.35, p_gap = 0.15) +
  labs(x = NULL, y = "Concentration", title = "Butyric Acid")
fig5 = plot_clme(summ_fit5, group = c("No", "Yes"),
                 y_min = 0, y_max = 0.12, p_gap = 0.05) +
  labs(x = NULL, y = "Concentration", title = "Isovaleric Acid")
fig6 = plot_clme(summ_fit6, group = c("No", "Yes"), 
                 y_min = -0.01, y_max = 0.02, p_gap = 0.01) +
  labs(x = NULL, y = "Concentration", title = "Valeric Acid")

p_clme2 = ggarrange(fig1, fig2, fig3, fig4, fig5, fig6, 
                    ncol = 6, common.legend = TRUE, legend = "bottom")
p_clme2
ggsave("../results/figures/supp_clme_plot_v1_decrease.jpeg", width = 12, height = 5, dpi = 100)
ggsave("../results/figures/supp_clme_plot_v1_decrease.pdf", width = 12, height = 5)
```

## 4.2 At 28 weeks {.tabset}

### Monotonic increasing trend

```{r, fig.width=12, cache=TRUE}
cons = list(order = "simple", decreasing = FALSE, node = 1)

fit1 = clme(Acetic ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit2 = clme(Propionic ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit3 = clme(Isobutyric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit4 = clme(Butyric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit5 = clme(Isovaleric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit6 = clme(Valeric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)

summ_fit1 = summary(fit1)
summ_fit2 = summary(fit2)
summ_fit3 = summary(fit3)
summ_fit4 = summary(fit4)
summ_fit5 = summary(fit5)
summ_fit6 = summary(fit6)

fig1 = plot_clme(summ_fit1, group = c("No", "Yes"), 
                 y_min = 0, y_max = 4.5, p_gap = 1.2) +
  labs(x = NULL, y = "Concentration", title = "Acetic Acid")
fig2 = plot_clme(summ_fit2, group = c("No", "Yes"), 
                 y_min = -0.1, y_max = 0.6, p_gap = 0.3) +
  labs(x = NULL, y = "Concentration", title = "Propionic Acid")
fig3 = plot_clme(summ_fit3, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.05, p_gap = 0.02) +
  labs(x = NULL, y = "Concentration", title = "Isobutyric Acid")
fig4 = plot_clme(summ_fit4, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.35, p_gap = 0.15) +
  labs(x = NULL, y = "Concentration", title = "Butyric Acid")
fig5 = plot_clme(summ_fit5, group = c("No", "Yes"),
                 y_min = 0, y_max = 0.08, p_gap = 0.03) +
  labs(x = NULL, y = "Concentration", title = "Isovaleric Acid")
fig6 = plot_clme(summ_fit6, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.02, p_gap = 0.01) +
  labs(x = NULL, y = "Concentration", title = "Valeric Acid")

p_clme1 = ggarrange(fig1, fig2, fig3, fig4, fig5, fig6, 
                    ncol = 6, common.legend = TRUE, legend = "bottom")
p_clme1
ggsave("../results/figures/supp_clme_plot_v2_increase.jpeg", width = 12, height = 5, dpi = 100)
ggsave("../results/figures/supp_clme_plot_v2_increase.pdf", width = 12, height = 5)
```

### Monotonic decreasing trend

```{r, fig.width=12, cache=TRUE}
cons = list(order = "simple", decreasing = TRUE, node = 1)

fit1 = clme(Acetic ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit2 = clme(Propionic ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit3 = clme(Isobutyric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit4 = clme(Butyric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit5 = clme(Isovaleric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)
fit6 = clme(Valeric ~ wheezing, 
            data = df_v2, constraints = cons, seed = 123)

summ_fit1 = summary(fit1)
summ_fit2 = summary(fit2)
summ_fit3 = summary(fit3)
summ_fit4 = summary(fit4)
summ_fit5 = summary(fit5)
summ_fit6 = summary(fit6)

fig1 = plot_clme(summ_fit1, group = c("No", "Yes"), 
                 y_min = 0, y_max = 4.5, p_gap = 1.4) +
  labs(x = NULL, y = "Concentration", title = "Acetic Acid")
fig2 = plot_clme(summ_fit2, group = c("No", "Yes"), 
                 y_min = -0.1, y_max = 0.55, p_gap = 0.3) +
  labs(x = NULL, y = "Concentration", title = "Propionic Acid")
fig3 = plot_clme(summ_fit3, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.05, p_gap = 0.02) +
  labs(x = NULL, y = "Concentration", title = "Isobutyric Acid")
fig4 = plot_clme(summ_fit4, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.35, p_gap = 0.15) +
  labs(x = NULL, y = "Concentration", title = "Butyric Acid")
fig5 = plot_clme(summ_fit5, group = c("No", "Yes"),
                 y_min = 0, y_max = 0.08, p_gap = 0.03) +
  labs(x = NULL, y = "Concentration", title = "Isovaleric Acid")
fig6 = plot_clme(summ_fit6, group = c("No", "Yes"), 
                 y_min = 0, y_max = 0.02, p_gap = 0.01) +
  labs(x = NULL, y = "Concentration", title = "Valeric Acid")

p_clme2 = ggarrange(fig1, fig2, fig3, fig4, fig5, fig6, 
                    ncol = 6, common.legend = TRUE, legend = "bottom")
p_clme2
ggsave("../results/figures/supp_clme_plot_v2_decrease.jpeg", width = 12, height = 5, dpi = 100)
ggsave("../results/figures/supp_clme_plot_v2_decrease.pdf", width = 12, height = 5)
```

# Session information

```{r, message = FALSE, warning = FALSE, comment = NA}
sessionInfo()
```



